---
title: " "
author: " "
date: " "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note:  

- Change the information in the yaml header above:  title, author, data.
- Make sure output is html_document.
- Once you are finished coding, clear your environment and run each chunk individually to make sure there are no errors.  (If necessary fix your code.) Once your code is error-free, click "knit" on the menu above. Your document should compile to HTML, provided that you have output set to "html_document."
- In the code chunk above ("setup") echo is set to TRUE.  This means that the code in your chunks will be displayed, along with the results, in your compiled document.
- Please delete these and other directions before compiling and submitting your assignment.

## Load packages and create empty data frame

```{r}
# Load packages
library(tidyverse) 

# Define n
n <- 1000

# Empty data frame for 1000 simulated days
data <- data.frame(day = seq(1:n),
                demand = NA, # demand in Rockport
                quantity = NA, # quanity sold
                price = NA, # price per pound
                cost = 10000, # cost of daily operations
                earnings = NA)

head(data)

```

Your goal in this project is to:

1. Fill in the dataset with random numbers drawn from the probability distributions defined in the case description---distributions for demand, quantity and price.

2. Use those numbers to compute earnings.

3. Summarize the earnings distribution to inform a business recommendation.

Note:  

1. This case is slightly different from the one in the tutorial in that quantity sold is a function of demand: if demand is greater than 3500 then quantity is 3500 otherwise it equals demand.  The mathematical notation used for this relationship in the case description---min(3500, D)---is NOT R code. There are various ways of creating the quantity variable but `ifelse()` works well.

2. Use set.seed(123) once before doing any simulation.  Why 123?  This is an arbitrary seed that controls a random process, making the results comparable.  People who share the seed will get the same results. R will increment the seed in a deterministic fashion every time you run a random process.  So if you simulate your random variables in a different order than the one stipulated in the empty dataframe that has been provided, you will get a different answer.  Is it wrong?  No, but your results will not be identical to those of your classmates.  For example:

```{r}
set.seed(123)
rnorm(1000) %>% mean()
rnorm(1000) %>% mean()

```

The means of the two samples are different (.016 vs. .042) because R has incremented the seed for the second sample. 

Compare to:


```{r}
set.seed(123)
rnorm(1000) %>% mean()

set.seed(123)
rnorm(1000) %>% mean()

```

3. Clint Conley has 50 boats, but we will be modeling earnings per boat.  (It would be simple enough to multiply your per boat results by 50 to get earnings for the fleet.)

## Questions

Lightly comment your code and use pipes for readability.

Use this code chunk to simulate demand, quantity and price, and then compute earnings. Make sure to use set.seed(123) before running any random process to ensure that your results are reproducible!

```{r}
set.seed(123)

```


### Q1

Plot simulated earnings.

```{r}

```

### Q2

What is P(F > 1375)?

```{r}

```

### Q3

What is P(F < 0)

```{r}

```

### Q4

What is the expected value (mean) of F?

```{r}

```


### Q5

What is your advice to Clint Conley?  Write one paragraph in which you argue a position. In your answer please incorporate the quantitative details from your simulation, and consider in particular the trade-off between risk and reward.